---
title: 'GG 606: Homework Weeks 1-2'
author: "Author: Julia K"
date: "Date: 2024-01-30"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true
    toc_depth: 4  
  collapsed: no 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### **Loading Necessary Items**
```{r WEEK TWO: (here)package, include=TRUE}
library(tidyverse)
library(janitor)
library(broom)
library(ggthemes)
library(RColorBrewer)

library(here)                        #set wd through project file (week 2 hw)
library(palmerpenguins)
#getwd() #loads rmarkdown folder, set through knit > project as directory 
```

```{r}
source(here("functions", "theme_juicy.R")) #load from 'functions' folder
theme_set(theme_juicy())                   #auto-apply as theme for plots
```
Did nothing about that warning that prints above.

```{r WEEK ONE: INTRODUCTION + penguins, include=TRUE}
penguins=penguins %>%         #created the dataset as a callable object
  glimpse()
```
### **Manipulating the Dataset** 

**What is it that we would want to know? What plot types can show us this?** \

I would want to know if penguin body mass (M/F) among species varies depending 
on the island that they're on (lots of different floating variables here).
```{r WEEK ONE: INTRODUCTION + penguins; view data, include=TRUE}
#Figure out how many different islands there are for each species (filter or tally)
penguins %>%                         #did not create a new object in env. 
dplyr::select (species, island) %>%  #create subset w/ only these two cols
distinct(species, island) %>%        #create combination of species and island
  group_by(species) %>%              #tally of islands (n) per species
  count() %>%
print()                              #three spp. only Adelie has three islands
```
 Can only plot Adelie body mass per island because it's the only species that has
data from more than one island. But because I'm curious...  

***Adelie:*** three islands (Biscoe, Dream, Torgersen) n (appears) = 44, 56, 52 \
***Chinstrap:*** only one island (Dream) n= 68 \
***Gentoo:*** only one island (Biscoe) n= 124 \

**Don't know if M/F for any given n, nor the year**
_______________________________________________________________________________

Okay... *now* what do I wanna know? 

Differences in body mass index of both male and females among islands. Is there 
a correlation between body mass index and flipper length (i.e., if you're bigger
do you have larger flippers)? Do these variables vary a lot throughout the years? \
Would have to breakdown groupings by: i. Year ii. Island iii. Gender
  
```{r WEEK ONE: INTRODUCTION + penguins; manipulate data, include=TRUE}
peng_adelie=penguins %>%                         #created adelie penguins subset 
filter(species == "Adelie") %>%
 na.omit() %>%                                  #this removes ALL rows with 1+ NA
  mutate(body_mass_lbs=(body_mass_g / 453.6)) %>% #new col convert grams to lbs
  #mutate(`sum`()) before brackets would put the total sum within the new col lol
  mutate(across(c('body_mass_lbs'), round, 2)) %>% #round new col 2 decimal places

# Want to add the total number of penguins measured per year:
# mutate(
# distinct(body_mass_lbs, flipper_length_mm, sex, year) #specific penguin
# group_by(year)               
# mutate(count()) %>%
#  ) %>% 
  print() 
```

Could not easily figure out how to add the `count()` summary function to the
data table... so, manually computed them then will write in for figure... 
*Whomp whomp :(*
```{r}
peng_adelie %>%
distinct(body_mass_lbs, flipper_length_mm, sex, year) %>%   #specific penguin
  group_by(year) %>%                   #tally of penguins (n) per year
  count() %>%                         
print()                                #these data counts check out (verified)       
```

Plot with manually positioned text labels:
```{r}
n_counts=data.frame (                 #create a subset dataframe of these values
  label=c("n= 44", "n= 48", "n= 50"), #text you want to add
  year  =c(2007, 2008, 2009),         #col name facet_wrapped by
  x    =c(7, 7, 7),                   #exact position on the x-axis per grid
  y    =c(207.5, 207.5, 207.5))       #exact position on the y-axis per grid            
```


### **Ploting the Data**
```{r WEEK ONE: INTRODUCTION + penguins; plotting data, include=TRUE}
peng_adelie_figure=peng_adelie %>%          #create figure as a callable object
ggplot() + 
  facet_wrap(vars(year), ncol=3) +               #create a grid w/ 3 columns 
  geom_point(aes(x=body_mass_lbs, y=flipper_length_mm, colour=island, shape=sex), 
  size=2) +
  geom_smooth(aes(x=body_mass_lbs, y=flipper_length_mm, colour=island), method = "lm", se=FALSE) +
  
scale_colour_brewer(name= "Island", palette="YlOrRd") +  #ColorRBrewer package

  
labs(title="Adelie Penguin Survey Samples (2007-2009)") +
  labs(x=expression(atop("Body Mass (lbs)")),  #not technically coding right?
         y=expression("Flipper Length (mm)")) +

theme(legend.position="top") +                    #select where the legend rests
theme(legend.key.size=unit(0.35, 'cm')) +         #decrease legend size
theme(legend.margin=margin(t=0.25, unit='cm')) +  #reduce legend margin

geom_text(data=n_counts, 
          mapping=aes(x=x, y=y, label=label), colour="white")#add n text to each plot
          #don't have the skillset on how to generate background square for text rn
  
print(peng_adelie_figure)
```

Graph gives a... positive linear correlation? But linear regression stats do not
return any significant values (?) \
Data seems to show an overall increase in flipper length, while body mass remains 
similar. 
```{r}
body_mass_x_flipper_length=peng_adelie %>%      #create new object from dataframe
  group_by(year)                                #group analysis by year
  do(body_mass_x_flipper_length,                #take new object
     glance(                                    #look at the linear regression 
       lm(flipper_length_mm ~ body_mass_lbs, data=.))) #target x predictor
summary(body_mass_x_flipper_length)
```


### **Saving the Data**
```{r WEEK ONE: INTRODUCTION + penguins; saving the data, include=TRUE}
ggsave(here("figures", "adelie_penguin_plot.png"), peng_adelie_figure,
       width = 190, height = 120, units = "mm")  
```

