---
title: "GG 606: Lecture Notes?"
author: "Julia K"
date: "2024-01-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(janitor)


library(palmerpenguins)
getwd()
```

*Body mass (x) vs. 
Line of best fit: treated in alphabetical order is default behavior inside R.
Numerically are not treated as a 1,2,3: means for similar variances amongst groups then 
means given their variance is the mean here within its variance. Line of best fit?
The slope here means fake units why LOBF fails here. Changing the units on the
x-axis allows data to be better sprea default is model one linear regression and 
all error is assumed in the y. 
LOBF minimizing teh sum of the data away from the line amongt all data points. SST
is being minimized. Error in measuring flipper length (dislike)... consider the 
stairway for a model 2 regression instead. Do yo want up and down x/y axis or whether
you want true distance from data points perpendicular to the axis (a+b=c) pizza slices. Model 1 regression vs. model 2 regression etc. what is it that you want to tell?

Not the confidence in the slope of intercept, but 95% of predictions would fall within
this CI. 

```{r}

```

```{r}

```

